DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-09-29 paper/intro.tex
minor revision

% DeepPicar introduction
In this paper, we present DeepPicar, a low-cost autonomous car
platform for research and education. From hardware perspective, 
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$200 in total).
The DeepPicar, however, employs state-of-the-art AI
techonologies, including a vision-based end-to-end control system that
utilizes a deep convolutional nueral network (CNN).
The network receives an image frame from a single forward
looking camera as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}. 
The network has 9 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is identifical to that of NVIDIA's DAVE-2
self-driving car~\cite{Bojarski2016}, which uses much more powerful
computer (NVIDIA's automotive specialized DRIV-PX
computer~\cite{drivepx}) than the Raspberry Pi~3.
We chose to use the Pi 3 not only because of its
affordability but also because it is representative
of today's mainstream low-end multicore platforms, found in
smartphones and other embedded devices.

>>>>

% DeepPicar introduction
In this paper, we present DeepPicar, a low-cost autonomous car
platform for research and education. From hardware perspective, 
DeepPicar is comprised of a Raspberry Pi 3 Model B quad-core
computer, a web camera and a RC car, all of which are affordable
components (less than \$200 in total).
The DeepPicar, however, employs state-of-the-art AI
techonologies, including a vision-based end-to-end control system that
utilizes a deep convolutional nueral network (CNN).
The network receives an image frame from a single forward
looking camera as input and generates a predicted steering angle
value as output at each control period in \emph{real-time}. 
The network has 9 layers, about 27 million connections
and 250 thousand parameters (weights).
The network architecture is identifical to that of NVIDIA's DAVE-2
self-driving car~\cite{Bojarski2016}, which uses much more powerful
computer (NVIDIA's automotive specialized DRIV-PX
computer~\cite{drivepx}) than the Raspberry Pi~3.
We chose to use the Pi 3 not only because of its
affordability but also because it is representative
of today's mainstream low-end embedded multicore platforms, found in
smartphones and other embedded devices.
